### 2021-09-30 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex

\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from-BW}
\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

\begin{specialtable}[H] 
    %[htbp]

@@

\end{paracol}
\begin{specialtable}[H] 
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lccccccc}
    \toprule
     &  & \textbf{C-LFR-PRE} & \textbf{C-LFR-PAR} &  &	\textbf{C-LFR-CIRC} &	& \\
    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
    \midrule
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	N/A	&	N/A	&	N/A	\\
    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	N/A	&	N/A	&	N/A	\\
    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	N/A	&	N/A	&	N/A	\\
    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	N/A	&	N/A	&	N/A	\\
    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	N/A	&	N/A	&	N/A	\\
    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	N/A	&	N/A	&	N/A	&	0.7245	&	98.25	&	244.2	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	N/A	&	N/A	&	N/A	\\
    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	N/A	&	0.6867	&	0.6867	&	N/A	&	N/A	&	N/A	\\
    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	N/A	&	N/A	&	N/A	&	N/A	&	N/A	\\
    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	N/A	&	N/A	&	N/A	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	N/A	&	N/A	&	N/A	\\
    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	N/A	&	N/A	&	N/A	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	N/A	&	N/A	&	N/A	\\
    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	N/A	&	N/A	&	N/A	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	N/A	&	N/A	&	N/A	\\
    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	N/A	&	N/A	&	N/A	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	N/A	&	N/A	&	N/A	\\
    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
    \bottomrule
    \end{tabular}
    }
\end{specialtable}
\begin{paracol}{2}
\linenumbers
\switchcolumn

\subsubsection{C-LFR-PRE}
The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES. The hot TES is at a temperature of $560^{\circ}$C, with a $10^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least $570^{\circ}$C. In cases where the turbine outlet temperature is less than $570^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger. For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of $595^{\circ}$C. With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S. As the temperature of the hot TES is raised above a value of $540^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible. The temperature in the hot TES is therefore set to a lower value of $540^{\circ}$C to allow for operation of this cycle. With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler. This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.

>>>>

%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles that do not contain the listed component and omit the associated values. 
\clearpage 
\mw{Check that the column breakdown and grouping is correct in what I've changed.}
\end{paracol}
\begin{specialtable}[H] 
    %[htbp]

@@

\subsubsection{C-LFR-PRE}
The TES charging technique with the turbine prior to the C2S heat exchanger, C-LFR-PRE, requires the temperature of the C2S inlet to be high enough to charge the hot TES. The hot TES is at a temperature of 560$^{\circ}$C, with a 10$^{\circ}$C approach temperature, therefore the inlet temperature to C2S is required to be at least 570$^{\circ}$C. In cases where the turbine outlet temperature is less than 570$^{\circ}$C, a isenthalpic valve bypasses flow from the high temperature turbine inlet and mixes with the low temperature turbine outlet raising the temperature prior to the C2S heat exchanger. For the C-LFR-PRE configuration to be viable, it requires a larger temperature than the set LFR HX outlet temperature of 595$^{\circ}$C. With this low of a LFR outlet temperature, 73.78\% of the flow is redirected around the turbine to raise the temperature prior to C2S. As the temperature of the hot TES is raised above a value of 540$^{\circ}$C, the amount of flow around the turbine approaches 100\% and balancing the turbine power to compressor power is infeasible. The temperature in the hot TES is therefore set to a lower value of 540$^{\circ}$C to allow for operation of this cycle. With heat storage efficiency maximized, 93.89\% of the flow is sent to the main compressor, rejecting 622 MW of heat out of the cycle through the precooler. This amount of rejected heat is reflected in a heat storage efficiency of 34.53\%, the lowest of all tested TES charging configurations.

\begin{specialtable}[H]  
    %[htbp]
    \caption{Calculated system parameters for charging cycle configurations with constrained (\textit{C}) and unconstrained (\textit{U}) lead-cooled fast reactor low-end temperature.\label{tab-charg}}
    \resizebox{\columnwidth}{!}{
    \begin{tabular}{lc|c|cc|ccc}
    \toprule
     &  & \textbf{C-LFR-PRE} & \multicolumn{2}{c|}{\textbf{C-LFR-PAR}}  &	\multicolumn{3}{c}{\textbf{C-LFR-CIRC}} \\
    \textbf{Definition} & \textbf{Variable} & \textit{C} & \textit{C} & \textit{C} & \textit{C} &	\textit{C}	&	\textit{C}\\
    \midrule
    Cold TES Temperature ($^{\circ}$C)	&	$T_{CS}$	&	390	&	390	&	440	&	390	&	410	&	440	\\
    LFR Inlet Temperature ($^{\circ}$C)	&	$T_{4,1C}$	&	400	&	400	&	400	&	400	&	400	&	400	\\
    Heat Storage Efficiency (\%)	&	$\eta_{heatstorage}$	&	34.53	&	45.30	&	45.30	&	99.92	&	89.66	&	74.29	\\
    Alternator Power (MW)	&	$\dot{W}_{A}$	&	0	&	0	&	0	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    PC Heat Transfer (MW)	&	$\dot{Q}_{PC}$	&	622	&	519.6	&	519.6	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    MC Power (MW)	&	$\dot{W}_{MC}$	&	142.3	&	118.9	&	118.9	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    RC Power (MW)	&	$\dot{W}_{RC}$	&	21.89	&	77.28	&	77.28	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Turbine Power (MW)	&	$\dot{W}_{T}$	&	164.2	&	196.2	&	196.2	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Chiller Heat Transfer (MW)	&	$\dot{Q}_{chill}$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	0.7245	&	98.25	&	244.2	\\
    MC Mass Flow Fraction (-)	&	$y_{1}$	&	0.9389	&	0.7844	&	0.7844	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    C2S Mass Flow Fraction (-)	&	$y_{2}$	&	$\cdot$	&	0.6867	&	0.6867	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    Valve Mass Flow Fraction (-)	&	$y_{5}$	&	0.7378	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR UA Value (MW/$^{\circ}$C)	&	$UA_{LTR}$	&	6.99	&	22.83	&	22.83	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Capacitance Ratio (-)	&	$CR_{LTR}$	&	0.6754	&	0.8473	&	0.8743	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Heat Transfer Rate (MW)	&	$\dot{Q}_{LTR}$	&	93.05	&	366.4	&	366.4	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    LTR Effectiveness (-)	&	$\varepsilon_{LTR}$	&	0.6384	&	0.8742	&	0.8742	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR UA Value (MW/$^{\circ}$C)	&	$UA_{HTR}$	&	41.69	&	42.69	&	42.69	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Capacitance Ratio (-)	&	$CR_{HTR}$	&	0.7531	&	0.8143	&	0.8143	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Heat Transfer Rate (MW)	&	$\dot{Q}_{HTR}$	&	1567	&	1160	&	1160	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    HTR Effectiveness (-)	&	$\varepsilon_{HTR}$	&	0.9695	&	0.9627	&	0.9627	&	$\cdot$	&	$\cdot$	&	$\cdot$	\\
    C2S UA Value (MW/$^{\circ}$C)	&	$UA_{C2S}$	&	9.04	&	8.037	&	14.24	&	48.29	&	43.16	&	35.63	\\
    C2S Capacitance Ratio (-)	&	$CR_{C2S}$	&	0.4735	&	0.7556	&	0.9339	&	0.8755	&	0.8599	&	0.8294	\\
    C2S Heat Transfer Rate (MW)	&	$\dot{Q}_{C2S}$	&	328	&	430.4	&	430.4	&	949.3	&	851.8	&	705.8	\\
    C2S Effectiveness (-)	&	$\varepsilon_{C2S}$	&	0.9368	&	0.8275	&	0.8307	&	0.9511	&	0.9459	&	0.9355	\\
    C2S Approach Temperature ($^{\circ}$C)	&	$\delta_{C2S}$	&	10	&	35	&	26.27	&	10	&	10	&	10	\\
    \bottomrule
    \end{tabular}
    }
\end{specialtable}
% \begin{paracol}{2}
% \linenumbers
% \switchcolumn
